\large Autonomous Exploration by Expected Information Gain from Probabilistic Occupancy Grid Mapping

### 2018-06-09 Conference/SIMPAR 2016/SIMPAR2016_after_reviewer_edits_before_shortening.tex
added Conference folder

Robotic mapping is the process of generating maps, which represent the environment in close proximity of a robot. The popular occupancy grid mapping representation provides information about the free and occupied space as the robot measures its surroundings~\cite{ThrBurFox05}. Occupancy grid mapping is commonly used while estimating robot location and orientation, known as simultaneous localization and mapping (SLAM). Several SLAM approaches are applied to a variety of problems when mobile robots traverse through an environment to generate a map, but the trajectories are assumed given (e.g.~\cite{ThrBurFox05,DurBai06,CheChe09}). A major problem is that an effective trajectory would be unavailable knowing little or nothing about an environment. 
Autonomous exploration solves this problem, by choosing robotic motion through uncertain space, while building a map that is used for subsequent navigation~\cite{Yam97}.
In this paper, robotic motion is chosen to increase knowledge about the map; a robot chooses a trajectory designed to maximize information gain of the occupancy grid map.

@@

Standing alone, the term $P(z_{c,l,k}|X_{1:t},Z_{1:t},x_c)$ from \refeqn{DiscExpEntropyRay} has a convoluted meaning because the depth $z_{c,l,k}$ does not directly depend on the map. However, we present a method to obtain this discretized probability. %Despite how this term is replaced with a normalizer in ~\cite{ThrBurFox05} replaces
Following the assumption that $z_{c,l}$ is discretized to known distances, the probabilities are proportional to their densities, as the area under the density curve is infinitesimal and fixed. Accounting for all cases, the probability is
\begin{align}
\label{eqn:ProbWithDelta}
P(z_{c,l,k}|X_{1:t},Z_{1:t},x_c)=\frac{p(z_{c,l,k}|X_{1:t},Z_{1:t},x_c)}{\sum_{i=1}^{n_{r,l}+1}p(z_{c,l,i}|X_{1:t},Z_{1:t},x_c)}.
\end{align}
Conveniently, this density corresponds to the inverse normalizer defined in \refeqn{BayesRuleRayISM},
\begin{align}
\label{eqn:DiscretizedProb}
p(z_{c,l,k}|X_{1:t},X_c,Z_{1:t})=\eta_{c,l,k}^{-1},
\end{align}
where $\eta_{c,l,k}^{-1}$ is defined in \refeqn{allEta}. However, instead of evaluating the $t$-th pose $X_t$ and measured ray $z_{t,l}$, we simply consider $X_c$ and ray depth $z_{c,l,k}$ based on histories $X_{1:t}$ and $Z_{1:t}$ to obtain the inverse normalizer,
\begin{align}
\label{eqn:allEtaAtC}
\eta_{c,l,k}^{-1}
&=
\sum_{i=1}^{n_{r,l}+1}\bigg\{\prod_{j=0}^{i-1}P(\bar{\mathbf{r}}_{l,j}|X_{1:t},Z_{1:t})\bigg\}\nonumber\\&\qquad\times p(z_{c,l,k}|\mathbf{r}_{l,i+},X_c)P(\mathbf{r}_{l,i}|X_{1:t},Z_{1:t}).
\end{align}
By substituting \refeqn{ProbWithDelta} and \refeqn{DiscretizedProb} into \refeqn{DiscExpEntropyRay}, the expected entropy at $X_c$ from individual measurement ray $z_{c,l}$ is
\begin{align}
\label{eqn:HRayComplete}
&\text{E}[H(P(m|X_{1:t},Z_{1:t},x_c,z_{c,l}))]=\left(\sum_{i=1}^{n_{r,l}+1}\eta_{c,l,i}^{-1}\right)^{-1}\nonumber\\&\quad\quad\times\sum_{k=1}^{n_{r,l}+1}\bigg\{H(P(m|X_{1:t},Z_{1:t},x_c,z_{c,l,k}))\eta_{c,l,k}^{-1}\bigg\},
\end{align}
where $\eta_{c,l,k}^{-1}$ is taken from \refeqn{allEtaAtC}.
Here, \refeqn{HRayComplete} provides the expected entropies for those cells inside the field of view of $r_l$. %; cells outside this reduced map are trivially changed by $0$ due to $z_{c,l}$.
The entropies of cells outside the field of view remain unchanged.

@@

Throughout the numerical example, the robot must make several important decisions on which actions to take. These actions are evaluated based on their expected information gains, not frontiers a predicted measurement scans. If the obstacles were known a priori, the motion planning problem could be solved with a smoother path; however, the autonomous exploration is based on only the information of the map that the robot generates, so the motion planning must be reevaluated repeatedly. Even with these limitations, the robot explores the vast majority of reachable space in the $500$ second period.

>>>>

Robotic mapping is the process of generating maps, which represent the environment in close proximity of a robot. The popular occupancy grid mapping representation provides information about the free and occupied space as the robot measures its surroundings~\cite{ThrBurFox05}. Occupancy grid mapping is commonly used while estimating robot location and orientation, known as simultaneous localization and mapping (SLAM). Several SLAM approaches are applied to a variety of problems when mobile robots traverse an environment to generate a map, but the robot actions assumed given (e.g.~\cite{ThrBurFox05,DurBai06,CheChe09}). A major problem is that generating an effective trajectory for the robot to follow would be unavailable knowing little or nothing about an environment. 
Autonomous exploration solves this problem, by choosing robotic motion through uncertain space, while building a map that is used for subsequent navigation~\cite{Yam97}.
In this paper, robotic motion is chosen to increase knowledge about the map; a robot chooses a trajectory designed to maximize information gain of the occupancy grid map.

@@

Standing alone, the term $P(z_{c,l,k}|X_{1:t},Z_{1:t},x_c)$ from \refeqn{DiscExpEntropyRay} has a convoluted meaning because the depth $z_{c,l,k}$ does not directly depend on the map. However, we present a method to obtain this discretized probability. %Despite how this term is replaced with a normalizer in ~\cite{ThrBurFox05} replaces
Following the assumption that $z_{c,l}$ is discretized to known distances, the probabilities are proportional to their densities, as the area under the density curve is infinitesimal and fixed. Accounting for all cases, the probability is
\begin{align}
\label{eqn:ProbWithDelta}
P(z_{c,l,k}|X_{1:t},Z_{1:t},x_c)=\frac{p(z_{c,l,k}|X_{1:t},Z_{1:t},x_c)}{\sum_{i=1}^{n_{r,l}+1}p(z_{c,l,i}|X_{1:t},Z_{1:t},x_c)}.
\end{align}
Conveniently, this density corresponds to the inverse normalizer defined in \refeqn{BayesRuleRayISM} as the denominator from Bayes' rule,
\begin{align}
\label{eqn:DiscretizedProb}
p(z_{c,l,k}|X_{1:t},X_c,Z_{1:t})=\eta_{c,l,k}^{-1},
\end{align}
where $\eta_{c,l,k}^{-1}$ is defined in \refeqn{allEta}. However, instead of evaluating the $t$-th pose $X_t$ and measured ray $z_{t,l}$, we simply consider $X_c$ and ray depth $z_{c,l,k}$ based on histories $X_{1:t}$ and $Z_{1:t}$ to obtain the inverse normalizer,
\begin{align}
\label{eqn:allEtaAtC}
\eta_{c,l,k}^{-1}
&=
\sum_{i=1}^{n_{r,l}+1}\bigg\{\prod_{j=0}^{i-1}P(\bar{\mathbf{r}}_{l,j}|X_{1:t},Z_{1:t})\bigg\}\nonumber\\&\qquad\times p(z_{c,l,k}|\mathbf{r}_{l,i+},X_c)P(\mathbf{r}_{l,i}|X_{1:t},Z_{1:t}).
\end{align}
By substituting \refeqn{ProbWithDelta} and \refeqn{DiscretizedProb} into \refeqn{DiscExpEntropyRay}, the expected entropy at $X_c$ from individual measurement ray $z_{c,l}$ is
\begin{align}
\label{eqn:HRayComplete}
&\text{E}[H(P(m|X_{1:t},Z_{1:t},x_c,z_{c,l}))]=\left(\sum_{i=1}^{n_{r,l}+1}\eta_{c,l,i}^{-1}\right)^{-1}\nonumber\\&\quad\quad\times\sum_{k=1}^{n_{r,l}+1}\bigg\{H(P(m|X_{1:t},Z_{1:t},x_c,z_{c,l,k}))\eta_{c,l,k}^{-1}\bigg\},
\end{align}
where $\eta_{c,l,k}^{-1}$ is taken from \refeqn{allEtaAtC}.
Here, \refeqn{HRayComplete} provides the expected entropies for those cells inside the field of view of $r_l$. %; cells outside this reduced map are trivially changed by $0$ due to $z_{c,l}$.
The entropies of cells outside the field of view remain unchanged.

@@

Throughout the numerical example, the robot must make several important decisions on which actions to take. These actions are evaluated based directly on their expected information gains, not frontiers or predicted measurement scans. If the obstacles were known a priori, the motion planning problem could be solved with a smoother path; however, the autonomous exploration is based on only the information of the map that the robot generates, so the motion planning must be reevaluated repeatedly. Even with these limitations, the robot explores the vast majority of reachable space in the $500$ second period.
